Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-04-27 CSM_poster/main.tex
remove contact info
edit method section

\textcolor{dblue!70}{\ding{228}} \underline{Assessing Performance} Predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. Resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were averaged over each iteration and assessed as performance indicators.

@@

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

% \setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
% \setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors
% 
% \begin{alertblock}{Contact Information}
% 
% \begin{itemize}
% \item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
% \item Email: \href{mailto:john@smith.com}{john@smith.com}
% \item Phone: +1 (000) 111 1111
% \end{itemize}
% 
% \end{alertblock}
% 
% \begin{center}
% \begin{tabular}{ccc}
% \includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
% \end{tabular}
% \end{center}

>>>>

\textcolor{dblue!70}{\ding{228}} \underline{Assessing Performance} Predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. Resulting Nagelkerke's $R^2$, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio (PLR) and p-value, were averaged over each iteration and assessed as performance indicators.

@@
